---
title: "ANOVA"
output:
  html_document: default
  pdf_document: default
date: '2022-05-29'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r imports, include=FALSE}
library(tidyr)
library(ggcorrplot)
library(ggpubr)
library(dplyr)
library(ggplot2)
library(tidytext)
```

```{r dataset, include = FALSE}
setwd("C:/Users/William/OneDrive - NTNU/Documents/FYSMAT/Applied statistics/DigiserData")
df <- read.csv("indices.csv", head=T, sep = ";")
df <- df[,-c(1,4)] #remove first bs index
df <- df[-217,] #remove "innovations" row


# Dividing data into the four different levels
lvl0 <- df %>%
  select(names(df)[nchar(names(df))>7 & nchar(names(df))<9])

lvl1 <- df %>%
  select(names(df)[nchar(names(df))>5 & nchar(names(df))<7])

lvl2 <- df %>%
  select(names(df)[nchar(names(df))>2 & nchar(names(df))<5])

lvl3 <- df %>%
  select(names(df)[nchar(names(df))>1 & nchar(names(df))<3])

#create a df with only DPSVI and country
df_idx_full <- data.frame(country =df$country, DPSVI = df$DPSVI)
df_idx <- 
  df_idx_full %>% group_by(country) %>% filter(n()>1)

```

Start of with test of normaility
```{r normality}
shapiro.test(df$DPSVI)
```
Do not reject normality of DPSVI distribution (p=0.95)


Do a test for homoscedasticity.
```{r Bartletts test}
barTest <- bartlett.test(DPSVI ~ country, data = df_idx)
barTest
```


After doing Bartletts test we assume equal variance between countries, and we can now do anova.
Anova: is there a difference in the mean of DPSVI of the countries.
```{r ANOVA}
aov <- aov(df$DPSVI ~ country, data = df)
summary(aov)
```
Anova reject null hypothesis of equal means between countries(as expected).



Find variance in DPSVI in each country(only looking at countries with more than 1 observation ofc => we need to remove 3 observations).
```{r label, options}
#split data by country, then apply empircal variance function on each grouo
split_country <- split(df_idx, df_idx$country)
res <- lapply(split_country, function(x){data.frame(var = var(x$DPSVI))}) 

#Fit result in a data frame
res <- do.call(rbind,res)
df_var <- data.frame(country=rownames(res), DPSVI = res$var)

#Plot Result
ggplot(df_var, aes(reorder(country, DPSVI), DPSVI)) +
  geom_col() +
  theme(axis.text.x=element_text(angle=40,hjust=1,vjust=0.5))
  
```












