---
title: "additional data corr"
output: html_document
date: '2022-07-17'
---

Putting together dataset without NAs
```{r}
library(tidyr)
library(ggcorrplot)
library(ggpubr)
library(dplyr)
setwd("C:/Users/William/OneDrive - NTNU/Documents/FYSMAT/Applied statistics/DigiserData")
data <- read.csv("indices2.csv", head=T, sep = ";", encoding="UTF-8",)
vars <- read.csv("eurostat/data/01_socioeconomic_data.csv", head=T, sep = ",", encoding="UTF-8",)
```

```{r}
vars_1 <- subset( vars, select = -X )
```

```{r}
df <- reshape(vars_1, idvar = "cities", timevar = "variables", direction = "wide")
```

```{r}
names(df)[names(df) == 'cities'] <- 'City_Code'
```

```{r}
df_merge <- merge(data, df, by ="City_Code", all.x = TRUE)
```

To remove columns/rows such that we keep the most cities.
Create some funcs for this
```{r functions}
ratiobars_cols <- function(df) {
  nas <- rep(1,ncol(df))
    for (i in 1:ncol(df)) {
    nas[i] <- sum(is.na(df[,i]))
  }
  nas <- nas/nrow(df_complete)
  barplot(nas, ylim=c(0,1))
 return(nas)
}

ratiobars_rows <- function(dataframe) {
  nas <- rep(1,nrow(dataframe))
  for (i in 1:nrow(dataframe)) {
    nas[i] <- sum(is.na(dataframe[i,]))
  }
  nas <- nas/ncol(dataframe)
  bars <- barplot(nas, ylim=c(0,1))
  return(list(rat = nas, plot =bars))
}

```
Plots are just for confirming that removal works, dont mind them.


```{r try2}
df_complete <- df_merge[,-c(1,2,4)]
#Remove variables, leave indicators
df_I <- df_complete %>% select(-contains(c("0V","1V","2V","3V","4V","5V","6V","7V","8V","9V")))

#dataset wo populations
#df_I <- df_I %>% select(-contains(c("DE1")))


a <- ratiobars_cols(df_I)
removeidx <- which(a >0.4)
df_I_clean <- df_I[,-removeidx]



a <- ratiobars_rows(df_I_clean)
removeidx <- which(a$rat >0.0001)
df_I_clean <- df_I_clean[-removeidx,]
ratiobars_rows(df_I_clean)




ratiobars_cols(df_I_clean)
ratiobars_rows(df_I_clean)
```

Remove characters from numericals
```{r polishing fd_i}
df_rdy <- df_I_clean[,-1]


df_mat <- data.frame(lapply(df_rdy, function(x) {
  gsub("e","",x)
}))
df_mat <- data.frame(lapply(df_mat, function(x) {
  gsub("d","",x)
}))
df_mat <- data.frame(lapply(df_mat, function(x) {
  gsub("p","",x)
}))
df_mat <- data.frame(lapply(df_mat, function(x) {
  gsub("b","",x)
}))


```


```{r more polish}
df_ordered <- df_mat[names(df_rdy)]

#remove more covariates

df_num <- data.frame(sapply(df_ordered, as.numeric))
removes <- which(colSums(is.na(df_num))>0)
df_num <- df_num[,-removes]
#check for nas
which(colSums(is.na(df_num))>0)
which(rowSums(is.na(df_num))>0)
```


Create a nice(readable) pdf, saved in working directory
```{r corrplot 2}
corr <- cor(df_num)
pdf("corrdeletepls.pdf", width = 20, height = 20)
ggcorrplot(corr)
dev.off()
```


```{r actual corrs}
Inds <- corr[31,32:54]
pos <- Inds >0.1
Inds[pos]

neg <- Inds < -0.1
Inds[neg]
```



POSITIVE CORRELATION WITH DPSVI
DE1085? = 0.20
DE1084? = 0.26
DE1073(Median pop age) = 0.19
DE1061(pop 35-44 tot) = 0.16
DE1059(pop 35-44 male) = 0.21
DE1049(pop 20-24 tot) = 0.12
DE1040(pop 0-4 tot) = 0.21
DE3002(one person households) = 0.23
EC1003(Economic active pop female) = 0.4
EC1002(Economic active pop male) = 0.28



NEGATIVE CORRELATION WITH DPSVI
DE1076(pop female 5-9) = -0.12
DE1060(pop 25-35 female) = -0.12
DE1028(pop 65-74 tot) = -0.21
DE1025(pop 55-64 tot) = -0.33



Thus, a city with high active economic population is correlated with high digitalization. Looks like it is especially important that the female are economically active.

Young populations are more likely to live in cities with higher digitization.

Cities with lower digitalization seems to have more women of age 25-35 and 5-9. Maybe it is linked to pregnancy? 

A last point is that cities with more one person households have a higher degree of digitalization. This is probably a result of young people living like this.


